
---
title: "Capstone Quiz I"
output: statsr:::statswithr_lab
---

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}
library(dplyr)
library(ggplot2)

```


<div id="instructions">
Complete all **Exercises**, and submit answers to **Questions** on the Coursera 
platform.
</div>

This initial quiz will concern exploratory data analysis (EDA) of the Ames Housing dataset.  EDA is essential when working with any source of data and helps inform modeling.

First, let us load the data:

```{r load}
load("ames_train.Rdata")
```


1. Which of the following are the three variables with the highest number of missing observations?
<ol>
<li> `Misc.Feature`, `Fence`, `Pool.QC` </li>
<li> <b>`Misc.Feature`, `Alley`, `Pool.QC`</b> </li>
<li> `Pool.QC`, `Alley`, `Fence` </li> 
<li> `Fireplace.Qu`, `Pool.QC`, `Lot.Frontage` </li>
</ol>
```{r Q1}
str(ames_train)
na_count <-sapply(ames_train, function(y) sum(length(which(is.na(y)))))
na_count <- data.frame(na_count)
na_count$names <- rownames(na_count)
na_count <- na_count %>% arrange(desc(na_count)) %>% filter(na_count > 0)

na_count

```

\fb{The R function `is.na(x)` will return a boolean that specifies whether x is NA.  The function `colSums` or the package dplyr can help aggregate the total number of missing observations.
This question refers to the following learning objective(s):
Use frequency tables and bar plots to describe the distribution of a variable.
}

2. How many categorical variables are coded in R as having type `int`?  Change them to factors when conducting your analysis.
<ol>
<li> 0
<li> 1
<li> 2
<li> <b>3</b>
</ol>

```{r Q2}
# MS.SubClass, Overall.Qual, Overall.Cond, 
ames_train$MS.SubClass <- as.factor(ames_train$MS.SubClass)
ames_train$Overall.Qual <- as.factor(ames_train$Overall.Qual)
ames_train$Overall.Cond <- as.factor(ames_train$Overall.Cond)

```

\fb{Examine the type of each variable using the `summary` or `str` functions.  Are there any variables that are coded as `int` that can only take on a finite number of values (i.e. the magnitude of the number does not matter)?  Count them.

This question refers to the following learning objective(s):
Identify variables as numerical and categorical.
}

3. In terms of price, which neighborhood has the highest standard deviation?  
<ol>
<li> <b>`StoneBr`</b>
<li> `Timber`
<li> `Veenker`
<li> `NridgHt`
</ol>

```{r Q3}
ames_train %>% group_by(Neighborhood) %>% summarise(SD = sd(price)) %>% arrange(desc(SD))

```

\fb{In dplyr, the `group_by` command allows you to calculate quantities for each group using the `summarise` command.  

This question refers to the following learning objective(s):
When describing the distribution of a numerical variable, mention its shape, center, and spread, as well as any unusual observations.
}


4. Using scatter plots or other graphical displays, which of the following variables appears to be the best single predictor of `price`?
<ol>
<li> `Lot.Area`
<li> `Bedroom.AbvGr`
<li> <b> `Overall.Qual`</b>
<li> `Year.Built`
</ol>

```{r Q4}
str(ames_train$Lot.Area)
str(ames_train$Bedroom.AbvGr) 
str(ames_train$Overall.Qual)
str(ames_train$Year.Built)

ggplot(ames_train, aes(x=Year.Built, y=price)) + geom_point()
ggplot(ames_train, aes(x=Lot.Area, y=price)) + geom_point()
ggplot(ames_train, aes(x=as.factor(Bedroom.AbvGr), y=price)) + geom_boxplot()
ggplot(ames_train, aes(x=as.factor(Overall.Qual), y=price)) + geom_boxplot()
#ggplot()


```

\fb{For each of the listed independent variables, create a scatterplot with the independent variable on the x-axis and `price` on the y-axis.  What seems to be the most linear?

This question refers to the following learning objective(s):
Use scatterplots for describing the relationship between two numerical variables making sure to note the direction (positive or negative), form (linear or non-linear) and the strength of the relationship as well as any unusual observations that stand out.

}


5. Suppose you are examining the relationship between `price` and `area`.  Which of the following variable transformations makes the relationship appear to be the most linear?
<ol>
<li> Do not transform either `price` or `area`
<li> Log-transform `price` but not `area`
<li> Log-transform `area` but not `price`
<li> <b>Log-transform both `price` and `area`</b>
</ol>

```{r Q5}
ggplot(ames_train, aes(x=area, y=price)) + geom_point()
ggplot(ames_train, aes(x=area, y=log(price))) + geom_point()
ggplot(ames_train, aes(x=log(area), y=price)) + geom_point()
ggplot(ames_train, aes(x=log(area), y=log(price))) + geom_point()

```

\fb{For each of the four options, visualize the relationship using a graphical device such as a scatterplot.  What seems to be the most linear?

This question refers to the following learning objective(s):
Recognize when transformations (e.g. log) can make the distribution of data more symmetric, and hence easier to model.
Use scatterplots for describing the relationship between two numerical variables making sure to note the direction (positive or negative), form (linear or non-linear) and the strength of the relationship as well as any unusual observations that stand out.
}


6. Suppose that your prior for the proportion of houses that have at least one garage is Beta(9, 1).  What is your posterior? Assume a beta-binomial model for this proportion.
<ol>
<li> Beta(954, 46)
<li> Beta(963, 46)
<li> Beta(954, 47)
<li> <b> Beta(963, 47)</b>
</ol>


```{r Q6}
nrow(ames_train)
nrow(ames_train %>% filter(Garage.Cars == 0))
nrow(ames_train %>% filter(Garage.Cars > 0))

```

\fb{Recall that if the prior is $Beta(\alpha,\beta)$, then the posterior with $x$ successes in $n trials$ is $Beta(\alpha+x,\beta+n-x)$.

This question refers to the following learning objective(s):
Make inferences about a proportion using a conjugate Beta prior:
}


7. Which of the following statements is true about the dataset?
<ol>
<li> Over 30 percent of houses were built after the year 1999.
<li> The median housing price is greater than the mean housing price.
<li> <b> 21 houses do not have a basement. </b>
<li> 4 houses are located on gravel streets.
</ol>

```{r Q7}
N <- nrow(ames_train)
A <- nrow(ames_train %>% filter(Year.Built > 1999))
A/N * 100 

median(ames_train$price) > mean(ames_train$price) 

nrow(ames_train %>% filter(is.na(Bsmt.Qual)))


```

\fb{For each of the statements, determine whether it is true or false by using functions such as `summary`, `sum`, or `median` to describe the distribution of a relevant variable.

This question refers to the following learning objective(s):
Describe the distribution of a single variable.
}

8. Test, at the $\alpha = 0.05$ level, whether homes with a garage have larger square footage than those without a garage.
<ol>
<li> <b> With a p-value near 0.000, we reject the null hypothesis of no difference. </b>
<li> With a p-value of approximately 0.032, we reject the null hypothesis of no difference.
<li> With a p-value of approximately 0.135, we fail to reject the null hypothesis of no difference.
<li> With a p-value of approximately 0.343, we fail to reject the null hypothesis of no difference.
</ol>

```{r Q8}
gar_FALSE <- ames_train %>% filter(Garage.Cars == 0)
gar_TRUE  <-  ames_train %>% filter(Garage.Cars > 0)

mean(gar_FALSE$area)
mean(gar_TRUE$area)

sd(gar_FALSE$area)
sd(gar_TRUE$area)
# H(0) mu = 1145 H(1) mu > 1145

1145 - qt(.975, df = nrow(gar_FALSE) - 1) * sd(gar_FALSE$area)/sqrt(nrow(gar_FALSE))
1145 + qt(.975, df = nrow(gar_FALSE) - 1) * sd(gar_FALSE$area)/sqrt(nrow(gar_FALSE))

qt(.95, df = nrow(gar_FALSE) - 1)
nrow(gar_FALSE)

1145 - 1.65 * sd(gar_FALSE$area)/sqrt(nrow(gar_FALSE))
1145 + 1.65 * sd(gar_FALSE$area)/sqrt(nrow(gar_FALSE))

(1492.251 - 1145.043) / (sd(gar_FALSE$area)/sqrt(nrow(gar_FALSE)))



```

\fb{Use a hypothesis test to compare two means.  Use a pooled standard error to estimate the p-value. 

This question refers to the following learning objective(s):
Use the t-distribution for inference on a single mean, difference of paired (dependent) means, and difference of independent means.
}


9. Using $\log$(`price`) as the dependent variable and including all observations, what is the highest $R^2$ that can be achieved using exactly two predictor variables? These variables may be any of the original covariates or log-transformations of the numeric covariates.
<ol>
<li> 0.743
<li> 0.752
<li> 0.755
<li> <b>0.760</b>
</ol>

```{r Q9}

str(ames_train)
colnames(ames_train)
head(ames_train)


X <- ames_train %>% select(-Utilities)

# create regression between each column in Y and X
lms <- lapply(colnames(X), function(y) {
  form <- paste0("log(price) ~ ", y)
  print(form)
  lm(form, data=X)
})

N <- as.data.frame(colnames(X))


summary(lms[[2]])$adj.r.squared
# lms is a list of lm objects, can access them via [[]] operator
# or work with it using apply functions once again
R <- sapply(lms, function(x) {
  summary(x)$adj.r.squared
})

XR <- as.data.frame(cbind(colnames(X), R))


XR %>% arrange(desc(R))

summary(lm(log(price)~Neighborhood+Overall.Qual, data=X))$adj.r.squared



```

\fb{Identify potential variables to include by looking at their individual $R^2$ values when regressed on $\log$(`price`).  Find the combination of two that maximizes the $R^2$.

This question refers to the following learning objective(s):
When describing the association between two or more numerical variables, evaluate direction, form, and strength.
Note that $R^2$ will increase with each explanatory variable added to the model, regardless of whether or not the added variable is a meaningful predictor of the response variable. 
}

10. For homes with square footage greater than 2000, assume that the number of bedrooms above ground follows a Poisson distribution with rate $\lambda$.  Your prior on $\lambda$ follows a Gamma distribution with mean 3 and standard deviation 1.  What is your posterior mean and standard deviation for the average number of bedrooms in houses with square footage greater than 2000 square feet?
<ol> 
<li> Mean: 3.61, SD: 0.11
<li> <b>Mean: 3.62, SD: 0.10</b>
<li> Mean: 3.63, SD: 0.09
<li> Mean: 3.63, SD: 0.91
</ol>

```{r Q10}
# type your code for Question 10 here, and Knit
area_gt_2000 <- ames_train %>% filter(area > 2000)

n <- nrow(area_gt_2000)
s <- sum(area_gt_2000$Bedroom.AbvGr)


lambda <- 3 # k * theta == mean
stddev <- 1 # theta * sqrt(k)

# k* = k + sum(xi)
# theta* = theta(n/theat+1)

t <- (1/3) / (n*1/3+1) 
t
k <- 9 + s
k

k*t
t*sqrt(k)

```

\fb{Since the Gamma distribution is conjugate to the Poisson distribution, the posterior will be Gamma with parameter value  $k + \sum x_i$ and $\theta/(n\theta+1)$, where $k$ and $\theta$ represent the parameters of the prior distribution.  Based on the prior mean and standard deviation, elicit the prior values of $k$ and $\theta$.

This question refers to the following learning objective(s):
Make inferences about data coming from a Poisson likelihood using a conjugate Gamma prior.
Elicit prior beliefs about a parameter in terms of a Beta, Gamma, or Normal distribution.
}


11. When regressing $\log$(`price`) on $\log$(`area`), there are some outliers.  Which of the following do the three most outlying points have in common?
<ol> 
<li> They had abnormal sale conditions.
<li> They have only two bedrooms.
<li> They have an overall quality of less than 3.
<li> <b> They were built before 1930. </b>
</ol>

```{r Q11}
ggplot(ames_train, aes(x=log(area), y=log(price))) + geom_point()
x <- lm(log(price)~log(area), data=ames_train)
plot(x)
window()
plot(ames_train$area, cooks.distance(x))


a <- ames_train[c(206, 428, 741),]
b <- ames_train[c(310, 559),]

a$Sale.Condition
b$Sale.Condition

a$Bedroom.AbvGr
b$Bedroom.AbvGr

a$Overall.Qual
b$Overall.Qual

a$Year.Built
b$Year.Built

```

\fb{To identify the outliers, find the observations with the highest squared residuals under the proposed model.  Compare those observations (extract with the `which` function) to see what they have in common.

This question refers to the following learning objective(s):
Identify outliers and high leverage points in a linear model.
}


12. Which of the following are reasons to log-transform `price` if used as a dependent variable in a linear regression?
<ol> 
<li> `price` is right-skewed.
<li> `price` cannot take on negative values.
<li> `price` can only take on integer values.  
<li> <b> Both a and b.</b>
</ol>

```{r Q12}
x <- lm(price~area, data=ames_train)
plot(x)


```


\fb{We assume that residuals are normally distributed and can theoretically take on any value.  However, since `price` much be greater than 0 and right-skewed, the residuals are truncated and the assumption of normality is violated.  

This question refers to the following learning objective(s):
Identify the assumptions of linear regression and assess when a model may need to be improved.
}

13. How many neighborhoods consist of only single-family homes? (e.g. `Bldg.Type` = `1Fam`)
<ol> 
<li> 0
<li> 1
<li> 2 
<li><b> 3 </b>
</ol>

```{r Q13}
nrow(ames_train %>% group_by(Neighborhood) %>% summarise(bldg=mean(Bldg.Type=="1Fam")) %>% filter(bldg == 1.0) )
```

\fb{Use either frequency tables for each neighborhood or the dplyr command `group_by` followed by `summarise(mean(Bldg.Type == "1Fam"))`

This question refers to the following learning objective(s):
Use contingency tables and segmented bar plots or mosaic plots to assess the relationship between two categorical variables.
}

14. Using color, different plotting symbols, conditioning plots, etc., does there appear to be an association between $\log$(`area`) and the number of bedrooms above ground (`Bedroom.AbvGr`)? 
<ol> 
<li> Yes
<li> <b>No</b>
</ol>

```{r Q14}
cor(log(ames_train$area), ames_train$Bedroom.AbvGr)

ggplot(ames_train, aes(x=Bedroom.AbvGr, y=log(price))) + geom_point()

```

\fb{Find the correlation between the two variables.  Does there seem to be an association between the two?  Try plotting the relationship.

This question refers to the following learning objective(s):
Use scatterplots and other graphical devices to describe the relationship between two numerical variables.
}

15. Of the people who have unfinished basements, what is the average square footage of the unfinished basement?
<ol> 
<li> 590.36
<li> 595.27
<li> 614.37
<li> 681.94
</ol>

```{r Q15}


unf <- ames_train$Bsmt.Unf.SF

unf <- na.omit(unf)



sum(unf/999)
length(unf)


ames_train %>% filter(BsmtFin.Type.2 == "Unf" & BsmtFin.Type.1 == "Unf") %>% summarise(ma = mean(Bsmt.Unf.SF))

```

\fb{Remove all `NA` observations for the square footage of the unfinished basement and then find the mean of the remaining observations.

This question refers to the following learning objective(s):
Describe the distribution of a single variable.
}
